Reformulating phylogenetic mixed models to improve flexibility and speed

### 2018-09-13 main.tex
pushing yet another chart

% % \begin{table}
% % \begin{center}
% 
% \begin{tabularx}{\textwidth}{|X|X|X|}
% \hline
% Type of RE	& Formula	& Platform	\\
% \hline
% 
% Single site intercept	  &	1 $\mid$ sp	& gls (if residual = 0), phyloglm, \pkg{lme4} \\
% Single site intercept and uncorrelated slopes		&  1 $\mid$ sp + trait $\mid$ sp		& \pkg{lme4} \\
% Single site intercept and correlated slopes 			& 1 + trait $\mid$ sp					& \pkg{lme4} \\
% \hline
% Multiple site intercept 									&  1 $\mid$ sp 						& \pkg{pez}, \pkg{lme4} \\
% Multiple site intercept and uncorrelated slopes 	&  1 $\mid$ sp + trait $\mid$ sp 		& \pkg{pez}, \pkg{lme4} \\
% Multiple site intercept and correlated slopes 	& 	1 + trait $\mid$ sp					& \pkg{lme4} \\
% \hline
% \end{tabularx}
% % \vspace{1in}
% % ditto with site interaction								& ditto above $\mid$ sp:site		& ditto above \\
% % \end{center}
% % \end{table}

>>>>

% \begin{table}
% \begin{center}

\begin{tabularx}{\textwidth}{|c||c|c|c|c|c|c|}
\hline
Package	& \small{nlme}	& \small{phylolm}	& \small{lme4/glmmTMB} & \small{pez} & \small{brms} & \small{MCMCglmm} \\
\hline
\hline
Single Site & & & & & & \\
Random effects & X & X & X & & X & X \\
\hline
Phylo intercept & X & X & X &  & X & X \\
Phylo slope &  &  & X &  & X & X \\
Phylo correlation &  &  & X &  & X & X \\
Residual & & X & X &  & X & X \\
\hline
\hline
Multiple Site & & & & & & \\
Random effects &  &  & X & X & X & X \\
\hline
Phylo intercept &  &  & X & X & X & X \\
Phylo slope &  &  & X & X & X & X \\
Phylo correlation &  &  & X &  & X & X \\
Phylo interaction & &  & X & X & X &  \\
Species intercept & &  & X & X & X & X \\
Species slope & & & X & X & X & X \\
Species correlation & &  & X &  & X & X \\
Residual & &  & X & X & X & X \\
\hline

\end{tabularx}
% \vspace{1in}
% ditto with site interaction								& ditto above $\mid$ sp:site		& ditto above \\
% \end{center}
% \end{table}
